---
title: "Analysis of the data from the Women's Survey in the 2019 GMIS"
author: "Ama Owusu-Darko"
date: "1st May, 2021"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

## Introduction

### Data from Ghana Malaria Indicator Survey 2019

```{r shared-code, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
source(here::here("code/functions.R"))

```

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
Sys.setenv(tz="GMT")
library(tidyverse)
library(haven)
library(survey)
library(srvyr)
library(flextable)
library(magrittr)

library(table1)
library(gtsummary)
```

#### Stata Data Preprocessing

To create categorical variable binary Living_Children, with 2 levels from v219-

-   "0 or No" (Zero living children)

-   "1 or Yes" (Living children plus current pregnancy)

```{r living_children, message=FALSE, warning=FALSE, include=FALSE}
#gen Living_Children=(v219 != 0)
#label define bi 0 "No" 1 "Yes"
#label values Living_Children bi
```

To create categorical variable binary Allow_mal_vaccine, with 2 levels by recoding s512 and removing don't know level

-   "No" (Not allow child to be vaccinated)

-   "Yes" (Yes will allow child to be vaccinated)

```{r allow_mal_variable, message=FALSE, warning=FALSE, include=FALSE}
#recode s512 (0 8 =0 "No") (1=1 "Yes"), gen (Allow_mal_vaccine)
```

```{r load_women_mal data, message=FALSE, warning=FALSE, include=FALSE}
women_malaria <- read_dta("data/women_malaria.dta")
#View(women_malaria)
wm <- tibble(women_malaria)

```

#### Data Processing in R

Started with 5181 observations

-   Removed 1436 observations that is women without living children

    -   Removed 201 observations that is women whose age info v14 was not complete

Create new variable wm1 to preserve wm wm1 subset of data where living children== yes

```{r wm1_creation, message=FALSE, warning=FALSE, include=FALSE}
#create new variable wm1 to preserve wm
wm1=wm%>%
  filter(Living_Children==1)%>%
#Removed 1436 observations that is women without living children
  filter(v014==1)
#Removed 201 observations that is women whose age info v14 was not complete

#write data to stata
#write_dta(wm1,"Living_Children.dta")


# mutate(across(c(28,1513:1515,1739),drop_levels))
wm1%<>%
  mutate(across(c(16,17,28,29,47,62,63,73,84,462,463,1513:1515,1739,1740,1741),as_factor))%>%
  mutate(across(c(28,29,47,62,63,73,84),str_to_title))%>%
  mutate(across(c(16,17,28,29,47,62,63,73,84,462,463,1513:1515,1739,1740,1741),as_factor))%>%
  rename(Region=v024,
         Current_age=v012,
         Place_of_residence= v025,
         Religious_affiliation=v130,
         Gender_of_household_head = v151,
         Wealth_quintile=v190,
         Educational_level= v106,
         Living_children=v220,
         Age= v013)
  

summary(wm1[,c(16,17,28,29,47,62,63,73,84,462,1513:1515,1739,1740)])

#survey_set
women_svy<-wm1%>%
  as_survey_design(id=v021,strata=v023,weights=wgt)

```

```{r match_column index from labels, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
match("v024", names(wm1)) #column 28
match("s510", names(wm1)) #column 1513
match("s512", names(wm1)) #column 1515
match("s511", names(wm1)) #column 1514 #heard about malaria vaccine
match("Living_Children", names(wm1)) #column 1739
match("Allow_mal_vaccine", names(wm1))

match("v012", names(wm1)) #column 15 #current age
match("v014", names(wm1)) #column 17 #completeness of age info

match("v025", names(wm1)) #column 29 #urban or rural
match("v013", names(wm1)) #column 16 age in 5 year groups

match("v106", names(wm1)) #column 29 #factor educational level
match("v013", names(wm1)) #column 16 age in 5 year groups

#match("v025", names(wm1)) #column 29
match("v013", names(wm1)) #column 16 age in 5 year groups

match("v136", names(wm1)) #column 29 # household members
match("v137", names(wm1)) #column 16 number of children under 5 in the household at the time of the survey 

match("v220", names(wm1)) #column 463  living Children grouped
match("v013", names(wm1)) #column 16 age in 5 year groups


match("v130", names(wm1)) #column 62 religion
match("v131", names(wm1)) #column 63 ethnicity

match("v151", names(wm1)) #column 73 gender of household head
match("v190", names(wm1)) #column 84 wealth quintile

match("v219", names(wm1)) #column 462 living children not grouped

match("Ethinicity", names(wm)) #column 16 age in 5 year groups
```

#### Description of Variables

```{r description, message=FALSE, warning=FALSE, include=FALSE}
explanatory=tibble(Variable=c("Living Children"),
           `Operational Description` = c("Whether the Woman interviewed has living children"),
           `Scale of Measurement`= c("Binary"),Levels=c("Yes or No"))

response=tibble(Variable=c("Allow_mal_vaccine"),
           `Operational Description` = c("Will the womean allow her child to be vaccinated"),
           `Scale of Measurement`= c("Binary"),Levels=c("Yes or No"))

ft1 <-flextable(response)
ft2 <-flextable(explanatory)
```

```{r flextable, echo=FALSE}


ft1%<>%theme_vanilla()%>%
  set_caption(caption="Table 1.1- Description of response variable of interest")

ft1

#print(ft1, preview = "docx")

#save_as_docx("my table" = ft, path = "/path/to/file.docx")

ft2%<>%theme_vanilla()%>%
  set_caption(caption="Table 1.2- Description of explanatory variables of interest")

ft2
```

----- Survey Analysis----------------------------------

#### Tabulate Allow child to take malaria vaccine over Region

```{r 02_svy_tab, message=FALSE, warning=FALSE, include=FALSE}
#tabulate Living Children by know about mal vaccine and accept mal vaccine for child
#create output table with flextable package

allow_mal=women_svy%>%
              group_by(Region,Allow_mal_vaccine)%>%
              summarise(Percentage=round(survey_mean(),4)*100)%>%
              pivot_wider(names_from = Allow_mal_vaccine, 
                          values_from=Percentage)

allow_mal_df = allow_mal[, -c(2)]

ft3<- flextable(allow_mal_df)

ft3 %<>%theme_vanilla()%>%
  set_caption(caption="Table 1.3- Percentage of Women aged 15-49 in each region grouped by their choices about the Malaria vaccine")%>%
  color(j="Yes", color = "blue")%>%
  bold(j="Yes", bold = TRUE)%>%
   add_header_row(values =c(" ", " Allow Child to take Malaria Vaccine"),
                        colwidths=c(1,2))



svymean(~Allow_mal_vaccine, women_svy)
a=svymean(~Age, women_svy)


```


```{r merging_table_1, include=FALSE}
out1 <- women_svy%>%
          group_by(Age)%>%
          summarise(Percentage=round(survey_mean(),4)*100)

out2 <- women_svy%>%
          group_by(Educational_level)%>%
          summarise(Percentage=round(survey_mean(),4)*100)

out3 <- women_svy%>%
          group_by(Ethnicity)%>%
          summarise(Percentage=round(survey_mean(),4)*100)


out4 <- women_svy%>%
          group_by(Place_of_residence)%>%
          summarise(Percentage=round(survey_mean(),4)*100)

out5 <- women_svy%>%
          group_by(Gender_of_household_head)%>%
          summarise(Percentage=round(survey_mean(),4)*100)

out6 <- women_svy%>%
          group_by(Living_children)%>%
          summarise(Percentage=round(survey_mean(),4)*100)


out7 <- women_svy%>%
          group_by(Wealth_quintile)%>%
          summarise(Percentage=round(survey_mean(),4)*100)


t1 <- flextable(out1[,-c(3)])

t2 <- flextable(out2[,-c(3)])#%>%
  #set_header_labels(Percentage= " ")

#ftry <- flextable(data.table::rbindlist(t1$body$dataset,t2$body$dataset))%>%
  #set_header_labels(Age= " ",Educational_level= " ")%>%
 # align(j,align="left")
 
t3 <- flextable(out3[,-c(3)])
t4 <- flextable(out4[,-c(3)])
t5 <- flextable(out5[,-c(3)])
t6 <- flextable(out6[,-c(3)])
t7 <- flextable(out7[,-c(3)])
```


<br>

#### Table 1 Characteristics of participants

```{r Table_1, message=FALSE, warning=FALSE, include=FALSE}
#wm1%>%table1(~Current_age | Allow_mal_vaccine)

ft4 <- as_flex_table(wm1%>%
    select(Age, Educational_level, Ethnicity, Place_of_residence,Gender_of_household_head, Living_children,Wealth_quintile)%>%
    tbl_summary(
                statistic = all_continuous() ~ "{mean}")%>%
    bold_labels())
  #modify_header(all_stat_cols() ~ "({style_percent(p)}%)") %>%
  #add_n() %>%

t1 <-wm1%>%
    select(Age, Educational_level, Ethnicity, Place_of_residence,Gender_of_household_head, Living_children,Wealth_quintile)%>%
    tbl_summary(
                statistic = all_continuous() ~ "{mean}")%>%
    bold_labels()
  

wm1%>%
  select(Age, Allow_mal_vaccine,Educational_level, Ethnicity, Place_of_residence,Gender_of_household_head, Living_children,Wealth_quintile)%>%
  tbl_summary(by=Allow_mal_vaccine,
              statistic = all_continuous() ~ "{mean}")%>%
  modify_header(all_stat_cols() ~ "**{level}**<br>N =  {n} ({style_percent(p)}%)") %>%
  bold_labels() %>%
  modify_spanning_header(all_stat_cols() ~ "**Allow Child to take Malaria Vaccine**")
 #add_n() %>%
```

<br>

#### Table 1- Socio-Demographic Characteristics of the subset of Women's Survey data from the 2019 Ghana Malaria Indicator Survey

```{r ft4_output, message=FALSE, warning=FALSE, include=FALSE}
ft4 %<>%
  set_caption(caption="Table 1.4- Socio-Demographic Characteristics of Female Survey Participants")
#print(ft4, preview = "docx") 
#theme_vanilla()%>%
```


```{r t1, message=FALSE, warning=FALSE}
t1 
t2 
t3 
t4 
t5 
t6 
t7 
```

<br> Tabulate Living Children by know about mal vaccine and accept mal vaccine for child

```{r flextable output1, message=FALSE, warning=FALSE}
ft3


```


```{r tests, include=FALSE}

#class(wm1$Allow_mal_vaccine)
#class(wm1$Current_age)

wm1%>%
  select(Allow_mal_vaccine, Current_age)%>%
  summary()

wm1%>%
  select(Allow_mal_vaccine, Current_age)%>%
  filter(Allow_mal_vaccine== "No")%>%
  summary()

wm1%>%
  select(Allow_mal_vaccine, Current_age)%>%
  filter(Allow_mal_vaccine== "Yes")%>%
  summary()

wm1%>%
  select(Allow_mal_vaccine, Current_age)%>%
  filter(Allow_mal_vaccine== "No")%>%
  summary()



```
